Visual Search and Pre-crastination

### 2023-08-31 analysis/1_processing.Rmd
fixing spelling typo

```{r, message=FALSE}
# attach packages
#library(rethinking)
library(tidyverse)
library(patchwork)
#library(brms)
library(rstan)
library(tidybayes)
library(binom)
```

@@

```{r}
dat_p <- read_csv("../data/personsonality_q.csv")

>>>>

```{r, message=FALSE}
# attach packages
#library(rethinking)
library(tidyverse)
library(patchwork)
library(binom)
```

@@

```{r}
dat_p <- read_csv("../data/personality_q.csv")
